si: code and prose exploring Spatial Interaction models

### 2022-06-13 README.qmd
Update all URLs #20

<!-- badges: start -->
[![R-CMD-check](https://github.com/robinlovelace/si/workflows/R-CMD-check/badge.svg)](https://github.com/robinlovelace/si/actions)
<!-- badges: end -->

@@

```r
remotes::install_github("robinlovelace/si")
```

>>>>

<!-- badges: start -->
[![R-CMD-check](https://github.com/Robinlovelace/sim/workflows/R-CMD-check/badge.svg)](https://github.com/Robinlovelace/sim/actions)
<!-- badges: end -->

@@

```r
remotes::install_github("Robinlovelace/sim")
```
